---
title: "Assignment 2"
author: "Seleni Cruz and Juliette Verstaen"
date: "April 15, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, message=FALSE}
library(dplyr)
library(ggplot2)
library(lubridate)
library(ggpubr)
```

###Load data and summarize by year
```{r data}
source("almond_yield_anomaly.R")

data<- read.csv (here::here("data_assignment1.csv")) 
data$Date<- mdy(data$Date)

climate<-read.table("clim.txt") # can use read.table 

Year <- data%>%
  group_by(year)%>%
  summarize(tmax_c = mean(tmax_c),
            tmin_c = mean(tmin_c),
            precip = sum(precip), 
            no_months=length(unique(month))) #first and last month dont have full 12 months
```

###Plot temperature and precipitation time series 
```{r plots}
ggplot(data)+
  geom_line(aes(x=Date, y= tmin_c), color= "blue")+
  geom_line(aes(x=Date, y= tmax_c), color= "red")+
  labs(y= "temperature °C")+
  scale_x_date(date_labels = "%b/%Y")

ggplot(data, aes(x=Date, y= precip))+
  geom_line()+
  scale_x_date(date_labels = "%b/%Y")

```

###Run function with provided data
#### Temperature sensitivity analysis plot: 1000 simulations with random uniform temperature increases between 0 and 3 degrees celcius. Almond yield anomaly seem to not be sensitive to changes in temperature.
```{r run_function}

almond <-almond_yield_anomaly(data=data)
almond$results
almond$min
almond$max
almond$plot



```

###Run all crop function with provided data for other crops 

```{r}
allcrop_yield_anomaly(data=data, crop="Avocados")
allcrop_yield_anomaly(data=data, crop="Wine Grapes")
allcrop_yield_anomaly(data=data, crop="Table Grapes")
allcrop_yield_anomaly(data=data, crop="Oranges")
allcrop_yield_anomaly(data=data, crop="Almonds")
allcrop_yield_anomaly(data=data, crop="Walnuts")

```


